A new tidy data structure to support exploration and modeling of temporal data

### 2019-08-29 tsibble.Rmd
minor tweaks and cite ggplot2

The **tsibble** package not only provides a "tsibble" data object but also a domain specific language in R for transforming temporal data. It takes advantage of the wrangling verbs implemented in the **dplyr** package, and develops a suite of new tools for facilitating temporal manipulation for easing, primarily, two aspects: implicit missingness handlers and time-aware aggregations.

@@

The **ggplot2** package (as the implementation of grammar of graphics) builds a powerful graphical system to declaratively visualize data. The data underpinning of **ggplot2** is tidy data, and in turn tsibble integrates well with **ggplot2**. The integration encourages more flexible graphics for exploring temporal structures via index, and individual or group differences via key.

@@

Here, the `pedestrian` dataset [@ped], available in the **tsibble** package is used. It contains hourly tallies of pedestrians at four counting sensors in 2015 and 2016 in inner Melbourne. The pipe operator `%>%` introduced in the **magrittr** package [@R-magrittr] chains the verbs, read as "then". A sequence of functions are composed in a way that can be naturally read from left to right, which improves the code readability. This code is read as "take the pedestrian data, fill the temporal gaps, filter to 2016 measurements, then apply an arima model and forecast ahead 2 days."

>>>>

The **tsibble** package not only provides a tsibble data object but also a domain specific language in R for transforming temporal data. It takes advantage of the wrangling verbs implemented in the **dplyr** package, and develops a suite of new tools for facilitating temporal manipulation for easing, primarily, two aspects: implicit missingness handlers and time-aware aggregations.

@@

The **ggplot2** package [@wickham2009ggplot2] (as the implementation of grammar of graphics) builds a powerful graphical system to declaratively visualize data. The data underpinning of **ggplot2** is tidy data, and in turn tsibble integrates well with **ggplot2**. The integration encourages more flexible graphics for exploring temporal structures via index, and individual or group differences via key.

@@

Here, the `pedestrian` dataset [@ped], available in the **tsibble** package is used. It contains hourly tallies of pedestrians at four counting sensors in 2015 and 2016 in inner Melbourne. The pipe operator `%>%` introduced in the **magrittr** package [@R-magrittr] chains the verbs, read as "then". A sequence of functions are composed in a way that can be naturally read from left to right, which improves the code readability. This code is read as "take the pedestrian data, fill the temporal gaps, filter to 2016 measurements, then apply an ARIMA model and forecast ahead 2 days."
